### 2017-08-08 Tex_Dissertation/MSc_dissertation.tex
afterresults

\centering % used for centering table
\begin{tabular}{||c | c | c||} % centered columns (4 columns)
\hline %inserts double horizontal lines
Before TMVA (Number of events)  & After TMVA (Number of events) & $\%$  \\ \hline % inserts single horizontal line
3005   & 493    & 16 \\
17628  & 558    &  3.1 \\
113494 &  528  &  0.4 \\  
\hline
 %inserts single line
\end{tabular}
\label{table:nonlin} % is used to refer this table in the text
\end{table}

@@

>>>>

\begin{table}
\centering % used for centering table
\begin{tabular}{||c | c | c | c||} % centered columns (4 columns)
\hline %inserts double horizontal lines
       BDT      &Before TMVA ($N_{events}$)  & After TMVA ($N_{events}$) & $\%$  \\ \hline % inserts single horizontal line
Signal           & 3005     &  493       & 16 \\
SUSY background  & 17628    &  558       & 3.1 \\
SM background    & 113494   &  528       &  0.4 \\  
\hline
 %inserts single line
\end{tabular}
\label{table:nonlin} % is used to refer this table in the text
\end{table}

@@

The variables that TMVA found most important are exactly the same with those of the BDT method, namely:

\begin{enumerate}
 \item $\theta_{miss}$ : the polar angle of the missing momentum of the jets.
 \item $p_{T}$ : the missing transverse momentum.
 \item $\Delta \phi$ : the angle between the reconstructed tops.
 \item $cos\theta_{top}$.
\end{enumerate}

In the following stacked histogram, it can be seen the post GBDT reduction of background and in the table 
above, the number of events that passed (for both signal and background) are denoted.

\begin{figure}[ht!]
\centering
  \includegraphics[width=0.8\linewidth]{{images/postbdtcut_gbdt}.pdf}
  \caption{\scriptsize{}}
\end{figure}

\begin{table}
\centering % used for centering table
\begin{tabular}{||c | c | c | c||} % centered columns (4 columns)
\hline %inserts double horizontal lines
       GBDT      &Before TMVA ($N_{events}$)  & After TMVA ($N_{events}$) & $\%$  \\ \hline % inserts single horizontal line
Signal           & 3005     & 455       & 15 \\
SUSY background  & 17628    &  330      & 1.8 \\
SM background    & 113494   &  198      &  0.1 \\  
\hline
 %inserts single line
\end{tabular}
\label{table:nonlin} % is used to refer this table in the text
\end{table}
